Finch: Sparse and Structured Array Programming with Control Flow

### 2024-03-22 sections/eval.tex
Update on Overleaf.

\subsubsection{Finch Logic}
The Finch Logic language takes inspiration from relational algebra while incorporating the ordered nature of dimensions in sparse tensors. In this analogy,

>>>>

\subsubsection{Finch Logic}
The logical language takes inspiration from relational algebra while incorporating the ordered nature of dimensions in sparse tensors. This means that ev
